---
title: "Convergence with respect to VTACS multipolar order"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Convergence with respect to VTACS multipolar order}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
options(cli.num_colors = 1)
theme_set(egg::theme_article())
opts_chunk$set(echo = FALSE, warning=FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example checks the convergence of orientation-averaged cross-sections with respect the maximum multipolar order describing individual scatterers and translation of vector spherical waves. The structure consists of four gold spheres in water arranged in a helix.

```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input_4_4')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,400), width = "200px", height = "150px", default_material='gold')
```

This simulation uses the following `input` file
```{R tpl}
```


```{r read, cache=FALSE}
```

where `{n1}, {n2}` are replaced by `4,5,...` in each separate run. 


## Orientation-averaged results

We see that in this example the cross-sections require higher than 4 multipolar orders in both $n_1$ and $n_2$ to converge, especially at shorter wavelengths. Typically, one needn't set $n_2$, as the default value $n_1=n_2$ is accurate; this optional parameter is mostly a remnant from the initial development stages.

```{r oa}
```

-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
