---
title: "Polarised orientation-averaged local field intensities"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 4
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Polarised orientation-averaged local field intensities}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
library(egg)
library(ggforce)
# library(purrr)
library(ggplot2)
library(egg)
# library(grid)
# library(readr)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```


## Objective

This example illustrates the calculation of orientation-averaged local field intensities for separate circular polarisations, using the keyword `MapOaQuantity [p]`. The structure consists of a tetramer of Au spheres. Because the structure is chiral, the local fields depend on the handedness of the incident light, even after full orientation averaging.


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input_u')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,200), width = "200px", height = "150px", default_material='gold')
```
We run three simulations: 

- `MapOaQuantity unpolarised`: returns orientation-averaged near fields, also averaged over polarisation
- `MapOaQuantity polarised`, with `Incidence 0 0 0 1` triggering both L and R polarisations
- `MapOaQuantity polarised`, with `Incidence 0 0 0 2` triggering only R polarisation


```{bash input}
cat input_L
```

```{r read}
```

```{r load, cache=FALSE}
```

```{r plot, fig.height=10,fig.width=8}
```


-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
