---
title: "Polarised orientation-averaged local field intensities"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 4
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Polarised orientation-averaged local field intensities}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
library(egg)
library(ggforce)
# library(purrr)
library(ggplot2)
library(egg)
# library(grid)
# library(readr)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```


## Objective

This example illustrates the calculation of orientation-averaged local field intensities for separate circular polarisations, using the keyword `MapOaQuantity [p]`. The structure consists of a tetramer of Au spheres. Because the structure is chiral, the local fields depend on the handedness of the incident light, even after full orientation averaging.


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input_u')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(200,100,100), width = "200px", height = "150px", default_material='gold')
```
We run three simulations: 

- `MapOaQuantity unpolarised`: returns orientation-averaged near fields, also averaged over polarisation
- `MapOaQuantity polarised`, with `Incidence 0 0 0 1` triggering both L and R polarisations
- `MapOaQuantity polarised`, with `Incidence 0 0 0 2` triggering only R polarisation


```{bash input}
cat input_L
```

```{r load, cache=FALSE}
```

For a given (L) polarisation we obtain:

```{r readL}
```

For unpolarised incidence:

```{r readU}
```


For both polarisations:

```{r readP}
```


## Maps

We now map the orientation-averaged local electric and magnetic field intensity and local degree of optical chirality (LDOC) in the z=0 plane, for unpolarised excitation, and the difference between L and R polarisations. Note that only the unpolarised electric field intensity is displayed in log scale. The calculations inside the spheres are not reliable and therefore not displayed.

For unpolarised LDOC, we simply average the two polarisations, as no formula is readily available.

```{r plot, fig.height=10,fig.width=8}
```


-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
