---
title: "Convergence with respect to maximum multipole order of individual scatterers"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Convergence with respect to maximum multipole order of individual scatterers}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example checks the convergence of orientation-averaged cross-sections with respect the maximum multipolar order describing individual scatterers. The structure consists of four gold spheres in water arranged in a helix.


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input_1')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,200), width = "200px", height = "150px", default_material='gold')
```

This simulation uses the following `input` file
```{R tpl}
```

where `{nmax}` is replaced by `1,2,3,...` in each separate run. 

The output consists of a number of files, storing the far-field cross-sections for each order from 1 to $n_{1}$.


```{r read, cache=FALSE}
```

```{r fun}
```

## Convergence with Nmax

We see that in this example the cross-sections converge after only a few multipoles, and that the dipole term gives already a reasonable approximation of the spectral lineshape,

```{r oa}
```

## Convergence with "MultipoleOrder"

The study above used masking of individual T-matrices to restrict the maximum Nmax, keeping `MultipoleOrder = 6` constant in all simulations. This is more meaningful, since the `MultipoleOrder` keyword refers to the order of expansions in the multiple scattering calculation, which typically requires a larger cutoff to accurately translate spherical waves from one origin to another. If we were to look at the individual contributions of the multipoles appearing in the cluster's expansion as a whole, the convergence looks very different (and arguably has a less physical interpretation).

```{r naive}
```

-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
