---
title: "Chain with large separation"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Chain with large separation}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
options(cli.num_colors = 1)
theme_set(egg::theme_article())
opts_chunk$set(echo = FALSE, warning=FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example compares the calculation of cross-sections based on a common origin (Scheme 3) vs Stout's particle-centred scheme (2). The structure consists of a small chain of 4 gold spheres in water, with a variable (large) separation.


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input_200_0_1')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,300), width = "200px", height = "150px") 
```


```{r load, cache=FALSE}
```

This simulation uses the following `input` file
```{r tpl}
```

where `{comment_centred}` comments out (`#`) or not the keyword `ScattererCentredCrossSections` in each separate run, `{scheme}` is in `0,1,2,3`, and `{separation}` is replaced by `200, 500, 1000` nm. The results are stored in separate output folders and collated for comparison. 

```{r read}
```

## Fixed-orientation results

We compare the fixed-orientation cross-sections, with the results of `Scheme = 0, ScattererCentred` replotted in every panel for comparison (pale thick lines, assumed here to be "ground truth").

```{r fo, fig.height=7, fig.width=10}
```

We observe that Mackowski's scheme (3) produces incorrect results at large inter-particle separations. For Stout's schemes (1 and 2) the use of `ScattererCentredCrossSections` is required for correct results in these conditions.

-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
