---
title: "Angular dispersion"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Angular dispersion}
  %\VignetteEncoding{UTF-8}
---


```{r demo, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr)
suppressPackageStartupMessages(require(terms))
library(rhdf5)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example illustrates the calculation of far-field cross-sections for multiple angles of incidence. The structure consists of two silver spheres in water, and all parameters are kept to their default values. 


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
suppressPackageStartupMessages(require(terms))
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,200), width = "200px", height = "150px")
```

This simulation uses the following `input` file
```{bash input}
cat input
```

The command to run the example is simply

```
../../build/terms input > log
```

The full log contains basic details of the calculations, and finishes with the timing.

<details closed>
<summary> Show log file (click to open) </summary>
```{bash log}
head -n62 log
echo "..."
tail -n1 log
```
</details> <br />

The output consists of a single hdf5 file, storing the far-field cross-sections for each order from 1 to $n_{1}$ for orientation-averaged quantities (as in example 01), and for each angle of incidence for fixed-orientation quantities, preceded by their average,

<details closed>
<summary> Show file results.h5 (click to open) </summary>
```{r read}
```
</details> <br />

## Fixed-orientation results

The following files contain fixed-orientation cross-sections for X and Y linear polarisations,

```{r fol,fig.height=5}
```

Because we are rotating $\phi$ from 0 to 90 degrees, the two polarisations show the opposite trend as the incident electric field rotates from x to y.

-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
