---
title: "Importing T-matrices in TERMS"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    fig_width: 7
    fig_height: 3
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Importing T-matrices in TERMS}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr)
suppressPackageStartupMessages(require(terms))
library(patchwork)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective


This example illustrates how to use TERMS with input T-matrices in `.tmat.h5` format. The structure consists of a dimer of gold spheroids in a chiral configuration. The T-matrix of a spheroid was pre-computed with a separate program: [JCMsuite](https://jcmwave.com/jcmsuite) (a Finite-Element package; this T-matrix is [available in the T-matrix database](https://github.com/tfp-photonics/tmatrix_data_format)), or [SMARTIES](https://www.wgtn.ac.nz/scps/research/research-groups/raman-lab/numerical-tools/smarties) (a T-matrix method).


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
suppressPackageStartupMessages(require(terms))
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input_spheroid1')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,200), width = "200px", height = "150px") 
```

## SMARTIES T-matrix

The T-matrix file was previously created with [SMARTIES](https://www.wgtn.ac.nz/scps/research/research-groups/raman-lab/numerical-tools/smarties) using these parameters

<details>
```{bash smarties, echo=TRUE}
cat smarties.m
```
</details>


The input file for TERMS is

```{bash input}
cat input_spheroid1
```
Note that only `vacuum_wavelength` in nanometres is supported, and the wavelengths much match exactly. TERMS does not check the embedding medium, so it also the user's responsibility to ensure they are identical.


```{r read, cache=FALSE}
```

and produces an output file `smarties_dimer.h5` storing the simulated results. 

## JCMsuite T-matrix

For comparison, we also run the same simulation with a T-matrix obtained via Finite-element simulations using JCMsuite. Below is a plot comparing the results.



This simulation uses the following `input` file
```{bash input_smarties}
cat input_spheroid2
```

```{r plot, fig.height=7}
```


The two simulations show excellent agreement.

-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
