---
title: "Per-particle absorption"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 3
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Per-particle absorption}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
options(cli.num_colors = 1)
theme_set(egg::theme_article())
options(cli.num_colors = 1)
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example illustrates the calculation of orientation-averaged absorption spectra in homogeneous spheres, with three different methods. The structure consists of two gold spheres in water.

```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,150), width = "200px", height = "150px") 
```

This simulation uses the following `input` file
```{bash input}
cat input
```

Note that currently the partial absorptions following Mackowski are not orientation-averaged (analytically); we therefore use an external incident file with quadrature nodes and weights,

<details closed>
<summary> Show incidence file (click to open) </summary>
```{bash incidence}
cat incidence
```
</details> <br />

<details closed>
<summary> Show log file (click to open) </summary>
```{bash log}
cat log
```
</details> <br />

## Total cross-sections

We first retrieve the total cross-sections, as usual,

```{r total}
```

## Mackowski's partial cross-sections 

```{r partial}
```

## Stout's per-particle cross-sections 

```{r split}
```

## Comparison

```{r comparison}
```

-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
