---
title: "Analytical vs numerical angular averaging"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Analytical vs numerical angular averaging}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
options(cli.num_colors = 1)
theme_set(egg::theme_article())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

Here we compare analytical orientation averaging of far-field cross-sections with a numerical cubature (38 point Lebedev).

```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,300), width = "200px", height = "150px") 
```

```{r read, cache=FALSE}
```

This simulation uses the following `input` file
```{bash input}
cat input
```

Incidence angles and the corresponding weights are specified in an external file `incidence`,

<details closed>
<summary> Show incidence file (click to open) </summary>
```{bash incidence}
cat incidence
```
</details> <br />

The command to run the example is simply

```
../../build/terms input > log
```

The full log contains basic details of the calculations, and finishes with the timing.

<details closed>
<summary> Show log file (click to open) </summary>
```{bash log}
head -n22 log
echo "..."
tail -n1 log
```
</details> <br />

The output consists as usual of a number of files storing the far-field cross-sections, for each angle of incidence.

```{r fun}
```

```{r fo}
```

## Orientation-averaged results

We compare the analytical orientation-averaged spectra (solid lines), with the numerical cubature (dashed lines):
```{r comparison}
```

apart from the blue end of the spectrum, the accuracy is good.


-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
