---
title: "Local degree of optical chirality"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 4
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Local degree of optical chirality}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
options(cli.num_colors = 1)
theme_set(egg::theme_article())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

\usepackage{mathrsfs}
\newcommand{\ldoc}{\mathscr{C}}
\newcommand{\ldocbar}{\overline{\mathscr{C}}}
\newcommand{\ldocoa}{\langle\mathscr{C}\rangle}
\newcommand{\ldocoabar}{\langle\overline{\mathscr{C}}\rangle}

## Objective

This example illustrates on a very simple case the calculation of the local degree of optical chirality for a dimer of spheres. The structure consists of two gold spheres with radius 10nm and gap 5nm in water, the incident field is linear with angle $\pi/4$ and $3\pi/4$ and $\ldocbar$ is calculated at the resonance wavelength of the structure and all other parameters are kept to their default values.

```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,150), width = "200px", height = "150px") 
```

This simulation uses the following `input` file
```{bash input}
cat input
```

## LDOC maps at fixed incidence


```{r read}
```

```{r comparison}
```

## Orientation-averaged near-field and LDOC maps 

TERMS can also compute orientation-averaged near-field quantities, with the Keyword `MapOaQuantity`. This structure is not particularly good at enhancing the local degree of chirality, but we use it as a simple example to illustrate the results of this calculation. The following map shows the orientation averaged LDOC for L and R circular polarisations.


```{r oa}
```


-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
