---
title: "Absorption computed from internal field"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 3
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Absorption computed from internal field}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
options(cli.num_colors = 1)
theme_set(theme_grey())
options(cli.num_colors = 1)
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example compares the calculation of far-field absorption against that of internal electric field intensity, for a core-shell dimer. The calculation is done for a fixed incidence direction.

```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,150), width = "200px", height = "150px") 
```

The standard far-field simulation uses the following `input` file

```{bash input}
cat input
```

Note that the two particles are different: the first scatterer is a homogeneous Au sphere, artificially separated into two regions. The second scatterer is a `Au@Pd` core-shell.

## Total cross-sections

We first retrieve the total cross-sections, as usual,

```{r total, fig.height=2.5}
```

## Mackowski's partial cross-sections 

Formulas derived by Mackowski provide partial absorptions for individual spheres, which we average with a numerical cubature. We verify that the total coincides with the previous plot.

```{r partial, fig.height=4}
```


## Internal field intensity

Absorption can also be calculated from the internal electric field intensity as

$$
\sigma_\mathrm{abs}(\lambda) = \frac{2\pi}{n \lambda}\iiint_V \varepsilon''(\lambda) |\mathbf{E}(\mathbf{r})|^2 \,\mathrm{dV}
$$
with $n$ the refractive index of the incident medium, $\varepsilon''$ the imaginary part of the material's dielectric function, and $\mathbf{E}(\mathbf{r}$ the internal electric field.

We apply this formula below to the four distinct regions (2 cores, and 2 shells). The first step is to generate a grid of points for TERMS to compute the electric field intensity in the regions of interest. One could use a regular grid extending over a larger area, and select the different regions in post-processing, but this is not efficient as many points would have to be sampled, including in non-absorbing regions (ambient medium). Instead, we create a numerical cubature over the ball (or shell) region, by taking a cartesian product of a spherical cubature in $(\varphi, \theta)$, and a Gauss-Legendre quadrature over the radial range.
 
```{r volumes, fig.height=6}
```

We define 4 such cubatures, one for each region of interest, and convert the points to cartesian coordinates before exporting them in a `position` file for use in TERMS
 
<details closed>
<summary> Show positions file (click to open) </summary>
```{bash positions}
cat positions
```
</details> 

Note that TERMS will automatically detect the material region corresponding to each point, and return this information in the near-field map. This is helpful to combine multiple regions as in this example, without needing to run separate simulations, or keep track of each point ourselves.

The input file for this near-field simulation is shown below.

```{bash inputnf}
cat input_map
```

### Processing

The output near-field maps can be split by `volID` and `scatID` fields, corresponding to our four regions of interest. We visualise below the electric field intensity at the sampled points for the outer shell of scatterer 1,

```{r readnf, fig.height=5}
```


```{r processnf, fig.height=4}
```

From the volumetric intensity maps, we apply the integration formula by multiplying with the cubature weights, and compare the results to the partial absorption cross-sections obtained above.

```{r comparison, fig.height=4}
```

Note that we only sampled a few wavelengths for clarity, but the near-field calculation is relatively fast, especially with the reasonable number of points afforded by the use of an efficient cubature, and the use of `Scheme=0` for solving at fixed incidence.

-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
