---
title: "Partial absorption in a core-shell dimer"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 4
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Partial absorption in a core-shell dimer}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example illustrates the calculation of absorption spectra in core-shell particles, separately for each layer. The structure consists of two core-shell spheres `Au@Ag` in water, and for comparison we also simulate a dummy `Au@Au` core-shell structure with the same dimensions.

```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input_AuAu')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,150), width = "200px", height = "150px") 
```

This simulation uses the following `input` file
```{bash input}
cat input_AuAg
```

Note that currently the partial absorptions are not orientation-averaged (analytically); we therefore use an external incident file with quadrature nodes and weights,

<details closed>
<summary> Show incidence file (click to open) </summary>
```{bash incidence}
cat incidence
```
</details> <br />

<details closed>
<summary> Show log file (click to open) </summary>
```{bash log}
cat log1
```
</details> <br />

## Total cross-sections

We first retrieve the total cross-sections, as usual,

<details closed>
<summary> Show output structure (click to open) </summary>
```{r xsec}
```
</details> <br />

## Per-layer absorption

Additional files/fields in the form `csAbs4L_scat00{i}coat{i}` are created for each layered sphere, containing partial absorption cross-sections for  particle ${i}$, up to layer ${j}$, with columns for each angle of incidence and the weighted average,

To get the per-layer absorption we need to take the difference between successive coats.

```{r coats}
```

In this plot the total absorption and per-particle absorption for the core-shell coincide.

```{r comparison, fig.height=4}
```

The absorption in the Ag layer is maximum at the plasmon resonance of the dimer, the position of which is largely dictated by the gold cores.



-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
