---
title: "Far-field comparison with MSTM"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Far-field comparison with MSTM}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
library(ggplot2)
library(rhdf5)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example compares the results obtained with TERMS and MSTM for orientation-averaged far-field cross-sections of a helix of Au nanospheres. 

```{r read, cache=FALSE}
```


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(-200,200,500), width = "200px", height = "150px", default_material='gold')
```

This simulation uses the following `input` file
```{bash input}
cat input
```

where the helix geometry was obtained via the convenience R function: 
```{r eval=FALSE}
terms::cluster_helix(N = 8, a = 50, b=50, c=50, R0 = 120, pitch = 400, delta = pi/4)
```

The results are also shown for a comparable simulation using the [MSTM package (version 4)](https://github.com/dmckwski/MSTM), which implements the superposition T-matrix method for clusters of spheres (note that TERMS uses similar algorithms in `Scheme=3`). 

The MSTM simulation is run with a separate input file for each wavelength (here 400 nm)

```{bash mstmfile}
cat "400.inp"
```

## Comparison

```{r comparison}
```

Very good agreement is observed over the entire spectrum, even with such closely-spaced nanoparticles at resonance. 

-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
