---
title: "Circular dichroism for a fingers crossed dimer of gold nanorods"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Circular dichroism for a fingers crossed dimer of gold nanorods}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
library(rhdf5)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example illustrates the calculation of far-field spectra for a dimer of particles described by external T-matrix files. The structure consists of two prolate gold spheroids in water, oriented in a chiral "fingers crossed" configuration that yields strong optical activity.

```{r read, cache=FALSE}
```


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,200), width = "200px", height = "150px", default_material='gold')
```

This simulation uses the following `input` file
```{bash input}
cat input
```

The T-matrix file was previously created with [SMARTIES](https://www.wgtn.ac.nz/scps/research/research-groups/raman-lab/numerical-tools/smarties) using these parameters

```{bash smarties, echo=TRUE}
head -n14 smarties.m
```

The command to run the example is simply

```
../../build/terms input > log
```

The full log contains basic details of the calculations, and finishes with the timing.

<details closed>
<summary> Show log file (click to open) </summary>
```{bash log}
head -n62 log
echo "..."
tail -n1 log
```
</details> <br />

The output consists of a number of files, storing the far-field cross-sections for each order from 1 to $n_{1}$.

```{r fun}
```

## Orientation-averaged results

```{r oa}
```

This chiral dimer produces strong circular dichroism.


-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
