---
title: "Comparison of schemes"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Comparison of schemes}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr)
suppressPackageStartupMessages(require(terms))
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective 

This example checks for consistency of the four calculation schemes for the calculation of far-field cross-sections. The structure consists of four gold spheres in water arranged in a helix.


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
suppressPackageStartupMessages(require(terms))
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input_1')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,150), width = "200px", height = "150px") 
```

This simulation uses the following template
```{r tpl}
```

where `{scheme}` is replaced by `0,1,2,3` in each separate run. The results are stored in separate output folders and collated for comparison. Note that `Scheme=0` does not calculate orientation-averaged quantities.

## Orientation-averaged results

We first check that orientation-averaged cross-sections are consistent for Schemes 1 to 3,

```{r oa, fig.height=4}
```

## Fixed-orientation results

Similarly, we check the linear polarisation cross-sections at fixed orientation,

```{r fo, fig.height=4}
```


-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
