---
title: "Diffractive chain of spheres"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Diffractive chain of spheres}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr)
suppressPackageStartupMessages(require(terms))
library(ggplot2)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example considers a chain of 20 Au spheres with relatively large inter-particle separation, commensurate with the wavelength. A strong multiple scattering effect is predicted despite the large distances between scatterers, due to diffractive coupling. The particle-centred scheme (Stout) is required in this calculation, as expanding about a single origin would require prohibitively large multipolar orders for accurate translations (the cluster as a whole has a large size parameter).

```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
suppressPackageStartupMessages(require(terms))
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input_chain')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(-1000,-500,-500), width = "200px", height = "150px", default_material='gold')
```

This simulation uses the following `input` file
```{bash input}
cat input_chain
```

```{r read, cache=FALSE, results='hide'}
```

## Fixed-orientation results

We compare the fixed-orientation cross-sections to the single-sphere reference (scaled by the particle number),

```{r fo, fig.height=3}
```
