---
title: "Polarimetry: Stokes vectors, phase matrix"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 4
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Polarimetry: Stokes vectors, phase matrix}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning=FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example illustrates the degree of circular polarisation at different wavelengths and scattering angles ($\theta$). The structure consists of a helix of five prolate gold spheroids inside the water with semi-axes a = b = 30 nm and c = 50 nm. The helix axis is z, radius 100 nm, pitch 700 nm, and the angular-step $\delta = \pi / 4$. The following R utility function was used to model the geometry,

```{r struct, echo = TRUE, eval=FALSE}
terms::cluster_helix(N = 5, a = 30, b = 30, c = 50, R0 = 100, pitch = 700, delta = pi/4)
```

The structure is illuminated with a linear polarised plane wave along the x direction, and the wavevector along the z direction. 

```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,500), width = "200px", height = "150px", default_material='gold') 
```

This simulation uses the following `input` file
```{bash input}
cat input
```

Mode 3 triggers the calculation of polarimetric quantities, with output listed below.

```{r read}
```

The output field `diff_Sca_CS` contains the differential scattering cross-section for the scattering angles requested, while fields `Stokes_phase_Mat` and `Stokes_Sca_Vec` include data of Stokes phase matrix and Stokes scattering vector. The structure is chiral and therefore converts linear polarisation to partially-circular polarisation, which can be quantified in the ratio between $V$ and $I$ ($V/I$) or, for an $x$-polarised plane wave, as $(Z_{41}+Z_{42})/(Z_{11}+Z_{12})$. 


## Differential scattering cross-section

The data have the following format
```{r dsca}
```

## Phase matrix

The data have the following format
```{r phasematrix}
```

## Stokes scattering vector

The data have the following format
```{r stokes}
```

-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
