---
title: "Quadrimer vs two dimers"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 4
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Quadrimer vs two dimers}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
library(rhdf5)
library(ggforce)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example illustrates the import of a TERMS-exported collective T-matrix as an input (effective) scatterer. We compare the simulation of a quadrimer of spheres to that of two dimers (with the same geometry). 

```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input_quadrimer_ff')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(200,0,0), width = "200px", height = "150px", default_material='gold')
```

```{bash input}
cat input_twodimers_nf
```

```{r read, results='hide'}
```

## Near-field

```{r nf}
```

As expected, the local fields cannot be calculated within the circumbscribed sphere of a dimer described as an input T-matrix.

## Far-field

```{r ff}
```

remarkably, the far-field cross-sections are quite accurate even though the Rayleigh hypothesis is badly violated.

-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_

