---
title: "Single sphere"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 3
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Single sphere}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
library(dplyr)
options(cli.num_colors = 1)
theme_set(egg::theme_article())
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning =FALSE, comment='', tidy=FALSE, cache = FALSE)
do.call(knitr::read_chunk, list(path = "_run.R"))
```


## Objective 

This tivial example illustrates the calculation of far-field spectra for absorption, scattering, and extinction. The structure consists of a single gold sphere in water.

```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
 }
  </style>')

ge <- get_geometry('input')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,200), width = "200px", height = "150px")
```

This simulation uses the following `input` file

```{bash input}
cat input
```

The command to run the example is simply

```
../../build/terms input > log
```

The full log contains basic details of the calculations, and finishes with the timing.

<details closed>
<summary> Show log file (click to open) </summary>
```{bash log}
head -n62 log
echo "..."
tail -n1 log
```
</details> <br />


```{r read}
```

## Orientation-averaged results

The following files contain orientation-averaged cross-sections,
```{r oa, fig.height=3}
```


-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_