---
title: "Circular dichroism for a fingers crossed dimer of gold nanorods"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Circular dichroism for a fingers crossed dimer of gold nanorods}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr)
suppressPackageStartupMessages(require(terms))
library(ggplot2)
library(rhdf5)
library(R.matlab)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning =FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example compares the results of TERMS with a coupled-dipole approximation for the far-field properties of a chiral dimer of Au spheroids.

```{r read, cache=FALSE}
```


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
suppressPackageStartupMessages(require(terms))
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('input')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,200), width = "200px", height = "150px", default_material='gold')
```

This TERMS simulation uses the following `input` file
```{bash input}
cat input
```

as well as a second simulation with only the electric dipole term,

```{bash input_dip}
cat input_dip
```

The T-matrix file was previously created with [SMARTIES](https://www.wgtn.ac.nz/scps/research/research-groups/raman-lab/numerical-tools/smarties) using these parameters

```{bash smarties, echo=TRUE}
head -n14 smarties.m
```

```{r fun}
```

The coupled-dipole simulations were performed with a in-house implementation in Matlab, which we are in the process of documenting and porting to the Julia language at [`CoupledDipole.jl`](http://nano-optics.ac.nz/CoupledDipole.jl/dev/gettingstarted/).

## Orientation-averaged results

```{r oa}
```

This average cross-sections and circular dichroism are in good agreement, especially when TERMS uses only the electric-dipole term.


-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
