---
title: "TERMS logo"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    fig_width: 7
    fig_height: 2
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{TERMS logo}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr)
library(terms)
library(ggplot2)
library(ggforce)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
```

This example describes the process to create the TERMS logo.

1. Download the font bpdots
2. Write TERMS with this font

```{r geometry, fig.height=1.2}
ge <- get_geometry(input = 'input')
cl <- cluster_geometry(ge)

ggplot() +
  coord_equal() +
  geom_circle(data=ge, aes(x0=x,y0=y,r=r,group=label),
              inherit.aes=FALSE,
              colour='black', alpha=0.5, lwd=0.2,lty=1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_continuous(expand=c(0,0)) +
  theme_void()+
  theme(legend.position = 'none', legend.direction = 'horizontal')
```

3. Overlap circles on top, save as svg
4. Import coordinates and radii 

<details closed>
<summary> Show svg file (click to open) </summary>
```{bash svg}
tail -n+6 terms.svg
```
</details> <br />

5. Rescale dimensions to desired range of nanometres
6. Create input file with those scatterers


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
ge <- get_geometry('input')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,1500), width = "100%", height="50%") 
```


<details closed>
<summary> Show input file (click to open) </summary>
```{bash input}
cat input
```
</details> <br />

7. Run the simulation (with low Nmax!)
8. Export the field map as a png image

```{r map, out.width='600'}
do.call(knitr::include_graphics, list(path = 'nf_map.png'))
```

9. Load the image in SquiggleDraw (Processing) and tune the parameters as desired

```{r squiggle, out.width='600'}
do.call(knitr::include_graphics, list(path = 'squiggle.png'))
```

[(link to svg)](squiggle.svg)

10. Export as svg, load and rescale in Inkscape, draw

```{r axi, out.width='600'}
do.call(knitr::include_graphics, list(path = 'axidraw.jpg'))
```
