---
title: "Timings"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 4
    fig_caption: true
    includes:
      in_header: "../../inst/_x3d_header.html"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Timings}
  %\VignetteEncoding{UTF-8}
---

```{r demo, message=FALSE, echo=FALSE}
library(knitr)
library(terms)
options(cli.num_colors = 1)
theme_set(theme_grey())
opts_chunk$set(echo = FALSE, warning=FALSE,
               message=FALSE, comment='', 
               tidy=FALSE, cache = FALSE)
do.call(read_chunk, list(path = "_run.R"))
```

## Objective

This example considers the scaling of computational time with respect to key parameters:

- number of particles
- number of multipoles
- number of incidence angles
- solution scheme

The number of wavelengths simply scales the computation time for all other parameters, as everything needs to be re-calculated for each wavelength (assuming negligible input-output time, compared to the calculations).

## Parameters

```{r params}
```

The structure consists of a helix of gold spheres, with varying number of particles.


```{r show_cluster, echo=FALSE, results='asis', message=FALSE}
library(terms)
cat('  <style>
.x3d_scene {
float:right;
margin:0em;
 }
  </style>')

ge <- get_geometry('runs/input_10_1_16_1_1')
cl <- cluster_geometry(ge)
terms::x3d_scene(cl, viewpoint=c(0,0,300), width = "200px", height = "150px") 
```

```{r tpl}
```

The timings are collected from the log files, and stored with the corresponding subroutine name (and detail where applicable),

```{r read}
```

## Total timings

We first look at the total run time summaries, as a function of number of particles $Npart$, multipolar order $Nmax$, and number of incidence directions $Ninc$.

```{r fulltimings, fig.height=5, fig.width=10}
```


## Detailed timings (subroutines)

At `Verbosity > 0` we can also access the timings within subroutines, to break down the calculation and identify time-consuming steps.

```{r info1}
str(combined)
unique(combined$routine)
```

Some subroutines are broken down in more detail,
```{r info2}
unique(combined$detail)
```

### Varying number of particles

```{r detailedtimings_Npart, fig.height=6, fig.width=10}
```

Details of the `solve` subroutine are shown below

```{r detailedtimings_Npart_2, fig.height=6, fig.width=10}
```

We can make some general remarks,

- The Stout Scheme (2) solves recursively the multiple scattering problem, starting with a dimer, and adding one particle at a time. This is evident in the routine `calcTIJStout` which increases in time.
- Mackwoski's Scheme (3) is very performant across the board; in fact it is about as fast as solving the original coupled-system without seeking the collective T-matrix, with the advantage that it also calculates orientation-averaged properties

### Varying maximum multipole order

```{r detailedtimings_Nmax, fig.height=6, fig.width=10}
```

Details of the `solve` subroutine are shown below

```{r detailedtimings_Nmax_2, fig.height=6, fig.width=10}
```

The computational cost scales similarly for all Schemes and subroutines with respect to maximum multipolar order.

### Varying number of incidence directions

```{r detailedtimings_Ninc, fig.height=6, fig.width=10}
```

Details of the `spectrumFF` subroutine are shown below

```{r detailedtimings_Ninc_3, fig.height=6, fig.width=10}
```

Details of the `solve` subroutine are shown below

```{r detailedtimings_Ninc_2, fig.height=6, fig.width=15}
```

Solving a linear system for multiple incidences (right hand side) differs between `Scheme = 0` (direct solve) and the other schemes (which seek a collective T-matrix). This is visible in routine `solLinSys`, which shows linear scaling in `Scheme = 0` while Schemes 1, 2, 3 have almost constant performance.

Curiously, the total timings rise sharply between 1 and 50 incidence angles for some schemes, suggesting that another subroutine is doing substantial computations. This may point to a possible optimisation in the future.


-----

```{r cleanup}
```
_Last run: `r format(Sys.time(), '%d %B, %Y')`_
